---
title: "R Notebook"
output: html_notebook
---


```{r data grouping, filtering and completing}
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("readr")) install.packages("readr")
if (!require("readxl")) install.packages("readxl")
if (!require("ggplot2")) install.packages("ggplot2")
library(tidyverse)
library(readr)
library(readxl)
library(ggplot2)


# using readr
rki_df <- read_csv("input/RKI_COVID19.csv")
print(head(rki_df))

start_day <- as.Date("2020-03-01")
end_day <- as.Date("2020-04-01")
maxLag <- 20

# helper function: specify_decimal(0.1239249249294, 3) = 0.123
specify_decimal <- function(x, k) trimws(format(round(x, k), nsmall=k))

# RKI-quote: damit ergibt sich: Anzahl F???lle der aktuellen Publikation als Summe(AnzahlFall), wenn NeuerFall in (0,1); Delta zum Vortag als Summe(AnzahlFall) wenn NeuerFall in (-1,1)
per_county_and_day <- rki_df %>%
                      # time line for each Landkreis
                      group_by(IdLandkreis, Landkreis, Refdatum) %>%
                      filter(IstErkrankungsbeginn == 1) %>%
                      # do not include duplicates
                      summarise(NeueFaelle = sum(AnzahlFall[NeuerFall %in% c(0,1)])) %>%   
                      # convert date and drop hours, minutes and seconds
                      mutate(Refdatum = as.Date(Refdatum, format ='%Y/%m/%d')) %>%  
                      # generate the time span for all Landkreise (if no cases got reported 
                      # on a specific day, the landkreis is not mentioned)
                      complete(Refdatum = seq.Date(as.Date("2020-01-01"), max(Refdatum), by="day")) %>% 
                      # generated aggregate "faelle" in previous steps is <na>, replace it by 0 cases
                      mutate(NeueFaelle = replace_na(NeueFaelle, 0)) %>% 
                      # library magic, easy cumsum bulding (sum of all past cases per landkreis for a specific date)
                      mutate(GesamtFaelleLandkreis = cumsum(NeueFaelle))  

k <- rki_df %>%
  distinct(IdLandkreis)
k

per_county_and_day

```
```{r visualization}

# useless visualization
ggplot(per_county_and_day, aes(x=Refdatum, y=GesamtFaelleLandkreis))+ 
      geom_line(aes(group = Landkreis, color=per_county_and_day$Landkreis)) + 
      theme(legend.position = "none") +
      ggtitle("Gesamtanzahl Faelle pro Landkreis")



# Total infections per day
ggplot( per_county_and_day %>%
        group_by(Refdatum) %>%
        summarise(infections_per_day = sum(NeueFaelle)), aes(x=Refdatum, y=infections_per_day))+ 
      geom_line() + 
      theme(legend.position = "none") +
  ggtitle("Gesamtanzahl Neuinfektionen in ganz Deutschland")




ggplot( per_county_and_day %>%
          filter(Refdatum >= start_day & Refdatum <= end_day) %>%
        group_by(Refdatum) %>%
        summarise(infections_per_day = sum(NeueFaelle)), aes(x=Refdatum, y=infections_per_day))+ 
      geom_line() + 
      theme(legend.position = "none") +
    ggtitle("Neuinfektionen in ganz Deutschland im untersuchtem Bereich")




ggplot(per_county_and_day, aes(x=Refdatum, y=NeueFaelle))+ 
      geom_line(aes(group = Landkreis, color=per_county_and_day$Landkreis)) + 
      theme(legend.position = "none") +
      ggtitle("Neuinfektionen pro Landkreis")




per_county_and_day_range <- per_county_and_day %>%
          filter(Refdatum >= start_day & Refdatum <= end_day)

per_county_and_day_range

ggplot(per_county_and_day_range, aes(x=Refdatum, y=NeueFaelle)) + 
      geom_line(aes(group = Landkreis, color=per_county_and_day_range$Landkreis)) + 
      theme(legend.position = "none") +
      ggtitle("Neuinfektionen pro Landkreis im untersuchtem Bereich")
```

<h2>Landkreise Geo data</h2>

```{r}
# https://public.opendatasoft.com/explore/dataset/landkreise-in-germany/

geo_landkreise_raw<- read_delim("input/landkreise-in-germany.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)
head(geo_landkreise_raw)

# Transform "GeoPoint"- string to double values LAT and LON
landkreis_info_list <- geo_landkreise_raw %>%
  # CCa equals idLandkreis in RKI dataset! Wuhu!
  select(`Geo Point`, `Name 2`, `Cca 2`) %>%  
  mutate(
    #Stack overflow magic .sapply()
    LAT = as.double(sapply(strsplit(geo_landkreise_raw$`Geo Point`, ","), `[`, 1)),
    #Stack overflow magic .sapply()
    LON = as.double(sapply(strsplit(geo_landkreise_raw$`Geo Point`, ","), `[`, 2)) 
  ) %>%
  rename(Name = `Name 2`) %>%
  # Rename id column to match the RKI dataset
  rename(IdLandkreis = `Cca 2`)%>%
  # unselect string "GeoPoint" because it will not get used anymore
  select(-`Geo Point`)

landkreis_info_list

#Plot Landkreis position
landkreis_info_list %>%
  ggplot(aes(x=LON, y=LAT)) + 
  geom_point(alpha=1,  color="orange", size=0.5) + 
  coord_equal() + 
  ggtitle("LAT & LONG (Position) of each Landkreis")
```

<h2> weather dataset </h2>
```{r weather setup}
if (!require("rgeos")) install.packages("rgeos")
if (!require("geosphere")) install.packages("geosphere")
if (!require("readxl")) install.packages("readxl")
if (!require("zoo")) install.packages("zoo")
if (!require("sp")) install.packages("sp")

library(tidyverse)
library(geosphere)
library(readxl)
#library(rgeos)
library(zoo)
library(sp)

#All file paths
noaa_station_directory <- "input/station_directory.txt"
noaa_station_details <- "input/station_list_details.txt"

noaa_station_download_url <- "https://www.ncei.noaa.gov/data/global-summary-of-the-day/access/2020"

gsod_filenames <- read.table(noaa_station_directory, header = FALSE,
                             stringsAsFactors = FALSE,
                             col.names = c("file","last_modified","time","size"))


#Set up filenames for all stations
gsod_filenames <- gsod_filenames %>%
  mutate(station_id = sub(".csv", "", file)) %>%
  select(file, last_modified, station_id)

#Reading this fixed-width file is a mess
noaa_col_names <- c("USAF",
                    "WBAN",
                    "STATION_NAME",
                    "CTRY",
                    "ST",
                    "CALL",
                    "LAT",
                    "LON",
                    "ELEV_M",
                    "BEGIN",
                    "END")

#Get station locations
noaa_stations <- read_fwf(noaa_station_details, 
                              fwf_positions(c(1, 8, 14, 44, 49, 52, 58, 66, 75, 83, 92), 
                                            c(7,13, 43, 46, 51, 56, 65, 74, 82, 91, 99), 
                                            noaa_col_names),
                              skip = 1, col_types = "ccccccccccc")
noaa_stations
#Must filter by END > a few days ago
#Also filter by BEGIN < Jan 1
#Finally remove the bad stations

#Join location to file names 
noaa_stations <- noaa_stations %>%
  unite(usaf_wban, USAF, WBAN, sep="") %>%
  mutate(LAT = as.numeric(sub("\\+","", LAT)),
         LON = as.numeric(sub("\\+","", LON)),
         ELEV_M = as.numeric(sub("\\+","", ELEV_M)),
         BEGIN = as.Date(BEGIN, format = "%Y%m%d"),
         END = as.Date(END, format = "%Y%m%d")) %>%
  inner_join(gsod_filenames,
             by = c("usaf_wban" = "station_id")) %>%
  filter(BEGIN <= start_day + maxLag) %>%
  filter(END >= end_day + maxLag)

  
#Plot station locations
noaa_stations %>%
  filter(CTRY == "GM") %>%
  ggplot(aes(x=LON, y=LAT)) + 
  geom_point(data = noaa_stations, 
             aes(x=LON,y=LAT), 
             color = "orange", alpha = 0.2, size=0.4) +
  geom_point(alpha=1,  color="blue", size=0.4) + 
  coord_equal() + 
  ggtitle("NOAA GSOD Weather Station Locations (Blue = Stations in Germany)")
```


```{r}
# Plot weather stations and Landkreis position
landkreis_info_list[,c("LAT", "LON")]%>%
  ggplot(aes(x=LON, y=LAT)) + 
  geom_point(alpha=1, size=1, color = "orange") + 
  geom_point(data = noaa_stations, 
             aes(x=LON,y=LAT), 
             color = "blue", alpha = 0.8, size=0.7) +
  geom_point(x=13,y=52, color="red")+     # BERLIN just for orientation
  geom_point(x=7,y=51, color="red")+      # COLOGNEjust for orientation
  coord_fixed(ratio = 1, xlim = c(5.4,15.3), ylim = c(45,57)) +
  ggtitle("Landkreise (orange) and all GSOD weather stations (blue)")
```

Use german weather stations... Deutscher Wetterdienst (dwd)
```{r}
# station detail list: https://opendata.dwd.de/climate_environment/CDC/observations_germany/climate/daily/kl/recent/KL_Tageswerte_Beschreibung_Stationen.txt

dwd_station_details <- "input/german_station_list_details.txt"


dwd_col_names <- c("STATION_ID",   
                    "BEGIN",     
                    "END",
                    "STATION_HEIGHT",
                    "LAT",
                    "LON",
                    "STATION_NAME",
                    "BUNDESLAND")


#Get station locations
dwd_stations_raw <- read_fwf(dwd_station_details, 
                         fwf_widths(c(5,9,9,15,12,10,42,54), dwd_col_names),   #Praise jesus, it finally worked
                              skip = 2, col_types = "ccciddcc")  #c = string, i=integer, d= double

# transforming date from "19930112" to YYYY-mm-dd
dwd_stations <- dwd_stations_raw %>%
                          mutate(BEGIN = as.Date(BEGIN, "%Y%m%d"),
                                 END = as.Date(END, "%Y%m%d")) 

dwd_stations

# Select stations that recorded weather in corona timespan
dwd_station_list <- dwd_stations %>%
                    filter(BEGIN <= start_day - maxLag) %>%
                    filter(END >= end_day)




# Plot weather stations and Landkreis position
landkreis_info_list[,c("LAT", "LON")]%>%
  ggplot(aes(x=LON, y=LAT)) + 
  geom_point(alpha=1, size=1, color = "orange") + 
  geom_point(data = dwd_station_list, 
             aes(x=LON,y=LAT), 
             color = "blue", alpha = 0.8, size=0.7) +
  geom_point(x=13,y=52, color="red")+     # BERLIN just for orientation
  geom_point(x=7,y=51, color="red")+      # COLOGNEjust for orientation
  coord_fixed(ratio = 1, xlim = c(5.4,15.3), ylim = c(47.3,55)) +
  ggtitle("Landkreise (orange) and ALL DWD weather stations (blue)")






dwd_lonlat <- cbind(dwd_station_list$LON, dwd_station_list$LAT)

# For each landkreis... generate distance matrix, find nearest
for (i in 1:nrow(landkreis_info_list)) {
  #print(i) #for monitoring progress
  
  # For each county...
  this_landkreis_loc <- cbind(landkreis_info_list[i,"LON"], 
                           landkreis_info_list[i,"LAT"]) 
  
  # Get distances to all stations - in km
  # function from "geospehre"-library
  distance_to_stations <- distHaversine(this_landkreis_loc, dwd_lonlat)
  
  # Note closest station
  closest_ind <- which.min(distance_to_stations)
  closest_station_id <- dwd_station_list[closest_ind,"STATION_ID"]
  
  landkreis_info_list$closest_station_id[i] <- as.character(closest_station_id)
  landkreis_info_list$km_to_closest_station[i] <- distance_to_stations[closest_ind]/1000
  
} 

closest_dwd_stations <- dwd_station_list %>%
  filter(STATION_ID %in% landkreis_info_list$closest_station_id)

paste("DWD Stations that recorded in corona times: ", nrow(dwd_station_list))
paste("Number of Landkreise: ",nrow(landkreis_info_list))
paste("Number of closest stations", nrow(closest_dwd_stations))


# Plot weather stations and Landkreis position
landkreis_info_list[,c("LAT", "LON")]%>%
  ggplot(aes(x=LON, y=LAT)) + 
  geom_point(alpha=1, size=1, color = "orange") + 
 # geom_point(data = closest_dwd_stations, 
 #            aes(x=LON,y=LAT), 
  #           color = "blue", alpha = 0.8, size=0.7) +
  geom_point(x=13,y=52, color="red")+     # BERLIN just for orientation
  geom_point(x=7,y=51, color="red")+      # COLOGNEjust for orientation
  coord_fixed(ratio = 1, xlim = c(5.4,15.3), ylim = c(47.3,55)) +
  ggtitle("Landkreise (orange)")

# Distribution of distances to closest station
landkreis_info_list %>%
  ggplot(aes(x=km_to_closest_station)) + 
  geom_histogram(binwidth=2 )
```


Download weather day summary data from closest stations.
1. Download .zip files and save into /download folder
2. Extract specific "produkt_klima_tag" file to /extract folder
```{r}
# https://opendata.dwd.de/climate_environment/CDC/observations_germany/climate/daily/kl/recent/tageswerte_KL_00044_akt.zip

options(timeout=3600)
# ONE TIME USE TO DOWNLOAD STATION DATA
## DOWNLOADS ALL DATA FROM STATIONS THAT STARTED RECORDING BEFORE 01.01.2020 AND AT LEAST UNTIL 01.06.2020
if(FALSE){
  for(id in dwd_station_list[1:50,1]){
    activity_url <- paste0("https://opendata.dwd.de/climate_environment/CDC/observations_germany/climate/daily/kl/recent/tageswerte_KL_", id ,"_akt.zip")
    #print(activity_url)
    dest_file <- paste0("download/",basename(activity_url))
    download.file(activity_url, destfile = dest_file)
    # only extract specific data file we are looking for
    # form: produkt_klima_tag_20181208_20200609_00142.txt
    
     zipped_csv_name <- grep('produkt_klima_tag_[:alnum:]*', unzip(dest_file, list=TRUE)$Name, 
                             ignore.case=TRUE, value=TRUE)
    
    unzip(dest_file, files=zipped_csv_name, exdir = "extract")
    }
}

# mydata <- read.csv(dir(pattern='/download/produkt_klima_tag_[:alnum:]*.txt')[1])
```

<h2>Sum up until now, we got:<h2>

Info to all landkreise:
landkreis_info_list <IdLandkreis, Name, LAT, LON, closest_station_id, km_to_closest_station>

Station meta data:
closest_dwd_stations <STATION_ID, BEGIN, END, STATIONS_HEIGHT, LAT, LON, STATION_NAME, BUNDESLAND>

Daily number of new cases for each landkreis, and cumsum until that date:
per_county_and_day <IdLandkreis, Landkreis, Refdatum, NeueFaelle, GesamtFaelleLandkreis>

All downloaded weather data in /extract folder in the form:
produkt_klima_tag_20181208_20200609_00044.txt  
where 00044 is the stationID.

```{r}
weather_data <- data.frame()

file_list <- list.files("extract/", pattern=".txt", full.names=T)
weather_data_raw <- do.call("rbind", lapply(file_list, read.csv, sep = ";"))

weather_data_processed <- weather_data_raw %>%
                rename(
                  stationID = STATIONS_ID,
                  recordingDate = MESS_DATUM,
                  qualityWindData = QN_3,
                  maxWindMS = FX,
                  dailyMeanWindMS = FM,
                  qualityRest = QN_4,
                  precipitationMM = RSK, #NiederschmaxLag
                  precipitationType = RSKF,
                  dailySunshineH = SDK,
                  dailySnowDepth = SHK_TAG,
                  dailyMeanOfCloudCover = NM,
                  dailyVaporPressureHPA = VPM,
                  dailyMeanPressure = PM,
                  dailyMeanTemp = TMK,
                  dailyMeanRelHumidity = UPM,
                  dailyMaxTemp = TXK,
                  dailyMinTemp = TNK,
                  dailyMinAirTemp = TGK
                ) %>%
                # mark all invalid values as NA
                mutate_all(na_if, -999) %>%
                # transform date from integer to date type 20200301 -> 2020-03-01
                mutate(recordingDate = as.Date(as.character(recordingDate), format ='%Y%m%d')) %>%
                # do not include end of data column, it is obsolete
                select(-c(eor)) %>%
                # on a mountain
                filter(stationID != 5792)


weather_data <- weather_data_processed %>%
               filter(recordingDate >= start_day - maxLag & recordingDate <= end_day)


r_start_day <-as.Date('2020-03-25')
r_end_day <- as.Date('2020-06-07')
weather_data_r <- weather_data_processed %>%
               filter(recordingDate >= r_start_day - maxLag  & recordingDate <= r_end_day)

summary(weather_data)
summary(weather_data_r)
timespan_days <- length(seq.Date(start_day - maxLag, end_day, by="day"))
timespan_days_r <- length(seq.Date(r_start_day - maxLag, r_end_day, by="day"))
paste("Number of days recording:",timespan_days)
paste("Number of days recording for r analysis:",timespan_days_r)


# HELPER FUNCTION
filterInvalidStations <- function(weatherFrame, col, timespanDays){
  tmp <-  weatherFrame[complete.cases(weatherFrame[ , col]), ]
  invalid_stations <- tmp %>%
              group_by(stationID) %>%
              filter(n() != timespanDays) %>%
              distinct(stationID)
  return (tmp  %>%
              filter(!(stationID %in% invalid_stations$stationID)))
}


# BY MEAN TEMPERATUR
weather_data_tmp <- filterInvalidStations(weather_data, "dailyMeanTemp", timespan_days)
weather_data_tmp_r <- filterInvalidStations(weather_data_r, "dailyMeanTemp", timespan_days_r)


weather_data_tmp %>%
  ggplot(aes(x=recordingDate, y=dailyMeanTemp, 
             group = factor(stationID))) + 
  geom_line(alpha = 0.04, color = "blue") + 
  ylab("Mean daily temperature (C??)") + 
  theme(legend.position = "none") + 
  ggtitle("Mean daily temperatur (all weather stations)")

weather_data_tmp %>% group_by(stationID) %>% summarise()
weather_data_tmp_r %>%
  ggplot(aes(x=recordingDate, y=dailyMeanTemp, 
             group = factor(stationID))) + 
  geom_line(alpha = 0.04, color = "blue") + 
  ylab("Mean daily temperature (C??)") + 
  theme(legend.position = "none") + 
  ggtitle("Mean daily temperatur (all weather stations)")
```

```{r}
# BY dailySunshineH !
weather_data_sunshine <- filterInvalidStations(weather_data, "dailySunshineH", timespan_days) 
weather_data_sunshine_r <- filterInvalidStations(weather_data_r, "dailySunshineH", timespan_days_r)


weather_data_sunshine %>%
  ggplot(aes(x=recordingDate, y=dailySunshineH, 
             group = factor(stationID))) + 
  geom_line(alpha = 0.04, color = "blue") + 
  ylab("Mean daily sunhine duration in hours") + 
  theme(legend.position = "none") + 
  ggtitle("Mean daily sunshine duration in H (all weather stations)")
```

```{r}
# BY dailyMeanWindMS !
weather_data_wind <- filterInvalidStations(weather_data, "dailyMeanWindMS", timespan_days) 
weather_data_wind_r <- filterInvalidStations(weather_data_r, "dailyMeanWindMS", timespan_days_r) 



weather_data_wind %>%
  ggplot(aes(x=recordingDate, y=dailyMeanWindMS, 
             group = factor(stationID))) + 
  geom_line(alpha = 0.04, color = "blue") + 
  ylab("mean wind velocity [m/s]") + 
  theme(legend.position = "none") + 
  ggtitle("Daily mean in wind velocity m/s (all weather stations)")
```
```{r}
# BY dailyMeanWindMS !
weather_data_humidity <- filterInvalidStations(weather_data, "dailyMeanRelHumidity", timespan_days) 
weather_data_humidity_r <- filterInvalidStations(weather_data_r, "dailyMeanRelHumidity", timespan_days_r) 

weather_data_humidity %>%
  ggplot(aes(x=recordingDate, y=dailyMeanRelHumidity, 
             group = factor(stationID))) + 
  geom_line(alpha = 0.04, color = "blue") + 
  ylab("daily mean of relative humidity in %") + 
  theme(legend.position = "none") + 
  ggtitle("Daily mean of relative humidity in % (all weather stations)")

```
```{r}
Nowcasting_Zahlen <- read_excel("input/Nowcasting_Zahlen.xlsx", 
    sheet = "Nowcast_R")
head(Nowcasting_Zahlen)

r_values <- Nowcasting_Zahlen %>%
          select(1,5,8,11)%>%
          rename(
             Erkrankungsbeginn = 1,
             Neuerkrankungen = 2,
             R = 3,
             R_7 = 4
          ) %>%
        filter(!is.na(R)) %>%
        filter(Erkrankungsbeginn >= r_start_day & Erkrankungsbeginn <= r_end_day)

r_values
```

```{r}
# HELPER FUNCTION

getMeanVector <- function(dataframe, col, shift){
  return (dataframe %>%
          group_by(recordingDate) %>%
          #!!!! IMPORTANT OPERATION. SHIFTING THE DATE OF RECORDING TO MATCH Refdatum! !!!!!
          mutate(recordingDate = (recordingDate+shift)) %>%
          summarise(mean = mean(get(col))))
}

joinResult_infections <- function(frameToJoin){
  return (per_county_and_day %>%
            filter(Refdatum >= start_day & Refdatum <= end_day) %>%
          group_by(Refdatum) %>%
          summarise(infections_per_day = sum(NeueFaelle)) %>%
          inner_join(frameToJoin,
               by = c("Refdatum" = "recordingDate")))
}

joinResult_r <- function(frameToJoin){
  return (r_values %>%
          filter(Erkrankungsbeginn >= r_start_day & Erkrankungsbeginn <= r_end_day) %>%
          inner_join(frameToJoin,
               by = c("Erkrankungsbeginn" = "recordingDate")))
}

fillCorList <- function(corList, resultFrame, shift, corMethod = "pearson"){
  corFac <- cor(resultFrame["infections_per_day"], resultFrame["mean"],  method = corMethod, use = "complete.obs")
  corList[[as.character(shift)]] <- corFac
  print(paste("shift: ",shift," cor: ", corFac))
}

drawTwoLinesGraph <- function(df,x,xlab, y1, y1_lab, y1_leg, y2, y2_leg, y2_lab, scale, title, lag, corList){
    ggplot(df, aes(x = x)) + 
      geom_line(aes(y = y1, colour = y1_leg))+
      geom_line(aes(y = mean*scale, colour = y2_leg))+
      scale_y_continuous(sec.axis = sec_axis(~./scale, name = ))+ 
      scale_colour_manual(values = c("blue", "red"))+ 
      labs(y = y1_lab,
                  x = xlab,
                  colour = "Parameter")+ 
      theme(legend.position = c(0.2, 0.87)) +
     ggtitle(paste(title, lag, "days; cor=",specify_decimal(corList[[as.character(lag)]],4)))
}
```


```{r}
lag_for_plot <- 7
lag_for_plot_r <- 7
tempCorList <- c()
tempCorList_r <- c()
for(i in seq(0,maxLag)){
  de_tmps <- getMeanVector(weather_data_tmp, col = "dailyMeanTemp", i)
  de_tmps_r <- getMeanVector(weather_data_tmp_r, col = "dailyMeanTemp", i)
  res <- joinResult_infections(de_tmps)
  res_r <- joinResult_r(de_tmps_r)
  
  if(i == lag_for_plot){
    resPlot <- res
  }
  
  if(i == lag_for_plot_r){
    resPlot_r <- res_r
  }
  tempCorList[[as.character(i)]] <- cor(res["infections_per_day"], res["mean"],  method = "pearson", use = "complete.obs")
  
  tempCorList_r[[as.character(i)]] <- cor(res_r["R"], res_r["mean"],  method = "pearson", use = "complete.obs")
}

tempCorList
barplot(tempCorList, ylim=c(-1,1), main = "Correleation with diff day shift: new cases ~ temperature")
barplot(tempCorList_r, ylim=c(-1,1), main = "Correleation with diff day shift: R ~ temperature")

drawTwoLinesGraph(resPlot, resPlot$Refdatum, "Date", resPlot$infections_per_day, "Infections per day", "Infections", resPlot$mean ,"Mean Temp in C??", "Mean Temp", 400, "Infections and mean temp", lag_for_plot, tempCorList)

drawTwoLinesGraph(resPlot_r, resPlot_r$Erkrankungsbeginn, "Date", resPlot_r$R, "R Value", "R", resPlot_r$mean ,"Mean Temp in C??", "Mean Temp", .05, "Infections and mean temp", lag_for_plot_r, tempCorList_r)
```

```{r}
lag_for_plot <- 7
lag_for_plot_r <- 5
sunCorList <- c()
sunCorList_r <- c()

for(i in seq(0,maxLag)){
  de_sun <- getMeanVector(weather_data_sunshine, col = "dailySunshineH", i)
  de_sun_r <- getMeanVector(weather_data_sunshine_r, col = "dailySunshineH", i)
  res <- joinResult_infections(de_sun)
  res_r <- joinResult_r(de_sun_r)
  
  if(i == lag_for_plot){
    resPlot <- res
  }
  if(i == lag_for_plot_r){
    resPlot_r = res_r
  }
  
  sunCorList[[as.character(i)]] <- cor(res["infections_per_day"], res["mean"],  method = "pearson", use = "complete.obs")
  sunCorList_r[[as.character(i)]] <- cor(res_r["R"], res_r["mean"],  method = "pearson", use = "complete.obs")
}
sunCorList
barplot(sunCorList, ylim=c(-1,1), main = "Correleation with diff day shift: new cases ~ sunshine duration")
barplot(sunCorList_r, ylim=c(-1,1), main = "Correleation with diff day shift: R ~ sunshine duration")

drawTwoLinesGraph(resPlot, resPlot$Refdatum, "Date", resPlot$infections_per_day, "Infections per day", "Infections", resPlot$mean ,"Mean sunshine duration in H", "Mean sunshine duration", 400, "Infections and mean sunshine duration", lag_for_plot, sunCorList)

drawTwoLinesGraph(resPlot_r, resPlot_r$Erkrankungsbeginn, "Date",resPlot_r$R, "R Value", "R", resPlot_r$mean ,"Mean sunshine duration in H", "Mean sunshine duration", 0.05, "Infections and mean sunshine duration", lag_for_plot_r, sunCorList_r)
```

```{r}
lag_for_plot <- 7
lag_for_plot_r <- 7
windCorList <- c()
windCorList_r <- c()
for(i in seq(0,maxLag)){
   de_wind <- getMeanVector(weather_data_wind, col = "dailyMeanWindMS", i)
  de_wind_r <- getMeanVector(weather_data_wind_r, col = "dailyMeanWindMS", i)
  res <- joinResult_infections(de_wind)
  res_r <- joinResult_r(de_wind_r)
  
     if(i == lag_for_plot){
    resPlot <- res
  }
  if(i == lag_for_plot_r){
    resPlot_r = res_r
  }
  
  windCorList[[as.character(i)]] <- cor(res["infections_per_day"], res["mean"],  method = "pearson", use = "complete.obs")
  windCorList_r[[as.character(i)]] <- cor(res_r["R"], res_r["mean"],  method = "pearson", use = "complete.obs")
}
windCorList

barplot(windCorList, ylim=c(-1,1), main = "Correleation with diff day shift: new cases ~ wind velocity")
barplot(windCorList_r, ylim=c(-1,1), main = "Correleation with diff day shift: R ~ wind velocity")



drawTwoLinesGraph(resPlot, resPlot$Refdatum, "Date", resPlot$infections_per_day, "Infections per day", "Infections", resPlot$mean ,"Mean wind velocity in m/s", "Mean wind velocity", 850, "Infections per day and mean wind velocity", lag_for_plot, windCorList)

drawTwoLinesGraph(resPlot_r, resPlot_r$Erkrankungsbeginn, "Date",resPlot_r$R, "R Value", "R", resPlot_r$mean ,"Mean wind velocity in m/s", "Mean wind velocity", 0.05, "Infections per day and mean wind velocity", lag_for_plot_r, windCorList_r)

```
```{r}
lag_for_plot <- 7
lag_for_plot_r <- 7
humCorList <- c()
humCorList_r <- c()

for(i in seq(0,maxLag)){
  de_humidity <- getMeanVector(weather_data_humidity, col = "dailyMeanRelHumidity", i)
  de_humidity_r <- getMeanVector(weather_data_humidity_r, col = "dailyMeanRelHumidity", i)
  res <- joinResult_infections(de_humidity)
  res_r <- joinResult_r(de_humidity_r)
  
  if(i == lag_for_plot){
    resPlot <- res
  }
  if(i == lag_for_plot_r){
    resPlot_r = res_r
  }
     humCorList[[as.character(i)]] <- cor(res["infections_per_day"], res["mean"],  method = "pearson", use = "complete.obs")
  humCorList_r[[as.character(i)]] <- cor(res_r["R"], res_r["mean"],  method = "pearson", use = "complete.obs")

}

barplot(humCorList, ylim=c(-1,1), main = "Correleation with diff day shift: new cases ~ rel. humidity")
barplot(humCorList_r, ylim=c(-1,1), main = "Correleation with diff day shift: R ~ rel. humidity")

humCorList

ylim.prim <- c(0, 6500) 
ylim.sec <- c(40, 80) 
b <- diff(ylim.prim)/diff(ylim.sec)
a <- b*(ylim.prim[1] - ylim.sec[1])

 ggplot(resPlot, aes(x = Refdatum)) + 
    geom_line(aes(y = infections_per_day, colour = "Infections"))+
    geom_line(aes(y = a + mean*b, colour = "Mean relative Humidity"))+
    scale_y_continuous(sec.axis = sec_axis(~ (. - a)/b, name = "Mean relative humidity in %??"))+ 
    scale_colour_manual(values = c("blue", "red"))+ 
    labs(y = "Infections per day",
                x = "Date",
                colour = "Parameter")+ 
   ggtitle(paste("Infections and mean rel. humidity with LAG=",lag_for_plot, "days; cor=",specify_decimal(humCorList[lag_for_plot],4)))
```

```{r}

Nowcasting_Zahlen <- read_excel("input/Nowcasting_Zahlen.xlsx", 
    sheet = "Nowcast_R")
head(Nowcasting_Zahlen)

rep_data <- Nowcasting_Zahlen %>%
          select(1,5,8,11)%>%
          rename(
             Erkrankungsbeginn = 1,
             Neuerkrankungen = 2,
             R = 3,
             R_7 = 4
          ) %>%
        filter(!is.na(R)) %>%
        filter(Erkrankungsbeginn > as.Date('2020-03-25') & Erkrankungsbeginn < as.Date('2020-06-07'))

rep_data

rep_data %>%
  ggplot(aes(x=Erkrankungsbeginn, y=R)) + 
  geom_line() + 
  ylab("R") + 
  theme(legend.position = "none") + 
  ggtitle("R-Value Germany")
```

